---
title: 'Results for age-specific/mobility renewal model'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  states:
    value: x
  JOBID:
    value: x
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, 'figure',  paste0(args$stanModelFile, "-",args$JOBID, "-", name, ".png"))
file.to.table = function(name) file.path(args$job_dir, 'table', paste0(args$stanModelFile, "-",args$JOBID, "-", name, ".rds"))
```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with jobid
```{r, echo=FALSE}
args$JOBID
```

## Results

### Expected deaths {.tabset .tabset-fade}

`r if ('AL' %in% args$states) '#### Alabama'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_AL"))){
  knitr::include_graphics(file.to.figure("posterior_predictive_checks_AL"))
}
```

`r if ('AK' %in% args$states) '#### Alaska'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_AK"))){
  knitr::include_graphics(file.to.figure("posterior_predictive_checks_AK"))
}
```

`r if ('AZ' %in% args$states) '#### Arizona'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_AZ"))){
  knitr::include_graphics(file.to.figure("posterior_predictive_checks_AZ"))
}
```

`r if ('AR' %in% args$states) '#### Arkansas'`
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_AR"))){
  knitr::include_graphics(file.to.figure("posterior_predictive_checks_AR"))
}
```

`r if ('CA' %in% args$states) '#### California'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_CA"))){
  knitr::include_graphics(file.to.figure("posterior_predictive_checks_CA"))
}
```

`r if ('CO' %in% args$states) '#### Colorado'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_CO"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_CO"))
}
```

`r if ('CT' %in% args$states) '#### Connecticut'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_CT"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_CT"))
}
```

`r if ('DE' %in% args$states) '#### Delaware'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_DE"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_DE"))
}
```

`r if ('DC' %in% args$states) '#### District of Columbia'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_DC"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_DC"))
}
```

`r if ('FL' %in% args$states) '#### Florida'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_FL"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_FL"))
}
```

`r if ('GA' %in% args$states) '#### Georgia'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_GA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_GA"))
}
```

`r if ('HI' %in% args$states) '#### Hawaii'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_HI"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_HI"))
}
```

`r if ('ID' %in% args$states) '#### Indiana'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_ID"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_ID"))
}
```

`r if ('IL' %in% args$states) '#### Illinois'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_IL"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_IL"))
}
```

`r if ('IN' %in% args$states) '#### Indiana'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_IN"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_IN"))
}
```

`r if ('IA' %in% args$states) '#### Iowa'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_IA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_IA"))
}
```

`r if ('KS' %in% args$states) '#### Kansas'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_KS"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_KS"))
}
```

`r if ('KY' %in% args$states) '#### Kentucky'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_KY"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_KY"))
}
```

`r if ('LA' %in% args$states) '#### Louisiana'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_LA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_LA"))
}
```

`r if ('ME' %in% args$states) '#### Maine'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_ME"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_ME"))
}
```

`r if ('MD' %in% args$states) '#### Maryland'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MD"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MD"))
}
```

`r if ('MA' %in% args$states) '#### Massachusetts'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MA"))
}
```

`r if ('MI' %in% args$states) '#### Michigan'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MI"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MI"))
}
```

`r if ('MN' %in% args$states) '#### Minnesota'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MN"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MN"))
}
```

`r if ('MS' %in% args$states) '#### Mississippi'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MS"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MS"))
}
```

`r if ('MO' %in% args$states) '#### Missouri'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MO"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MO"))
}
```

`r if ('MT' %in% args$states) '#### Montana'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_MT"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_MT"))
}
```

`r if ('NE' %in% args$states) '#### Nebraska'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NE"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NE"))
}
```

`r if ('NV' %in% args$states) '#### Nevada'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NV"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NV"))
}
```

`r if ('NH' %in% args$states) '#### New Hampshire'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NH"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NH"))
}
```

`r if ('NJ' %in% args$states) '#### New Jersey'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NJ"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NJ"))
}
```

`r if ('NM' %in% args$states) '#### New Mexico'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NM"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NM"))
}
```

`r if ('NY' %in% args$states) '#### New York'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NY"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NY"))
}
```

`r if ('NYC' %in% args$states) '#### New York City'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NYC"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NYC"))
}
```

`r if ('NC' %in% args$states) '#### North Carolina'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_NC"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_NC"))
}
```

`r if ('ND' %in% args$states) '#### North Dakota'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_ND"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_ND"))
}
```

`r if ('OH' %in% args$states) '#### Ohio'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_OH"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_OH"))
}
```

`r if ('OK' %in% args$states) '#### Oklahoma'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_OK"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_OK"))
}
```

`r if ('OR' %in% args$states) '#### Oregon'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_OR"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_OR"))
}
```

`r if ('PA' %in% args$states) '#### Pennsylvania'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_PA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_PA"))
}
```

`r if ('RI' %in% args$states) '#### Rhode Island'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_RI"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_RI"))
}
```

`r if ('SC' %in% args$states) '#### South Carolina'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_SC"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_SC"))
}
```

`r if ('SD' %in% args$states) '#### South Dakota'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_SD"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_SD"))
}
```

`r if ('TN' %in% args$states) '#### Tennessee'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_TN"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_TN"))
}
```

`r if ('TX' %in% args$states) '#### Texas'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_TX"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_TX"))
}
```

`r if ('UT' %in% args$states) '#### Utah'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_UT"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_UT"))
}
```

`r if ('VT' %in% args$states) '#### Vermont'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_VT"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_VT"))
}
```

`r if ('VA' %in% args$states) '#### Virginia'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_VA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_VA"))
}
```

`r if ('WA' %in% args$states) '#### Washington'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_WA"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_WA"))
}
```

`r if ('WV' %in% args$states) '#### West Virginia'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_WV"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_WV"))
}
```

`r if ('WI' %in% args$states) '#### Wisconsin'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_WI"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_WI"))
}
```

`r if ('WY' %in% args$states) '#### Wyoming'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("posterior_predictive_checks_WY"))){
knitr::include_graphics(file.to.figure("posterior_predictive_checks_WY"))
}
```


### Continuous age contribution {.tabset .tabset-fade}

`r if ('AL' %in% args$states) '#### Alabama'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_AL"))){
  knitr::include_graphics(file.to.figure("continuous_contribution_AL"))
}
```

`r if ('AK' %in% args$states) '#### Alaska'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_AK"))){
  knitr::include_graphics(file.to.figure("continuous_contribution_AK"))
}
```

`r if ('AZ' %in% args$states) '#### Arizona'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_AZ"))){
  knitr::include_graphics(file.to.figure("continuous_contribution_AZ"))
}
```

`r if ('AR' %in% args$states) '#### Arkansas'`
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_AR"))){
  knitr::include_graphics(file.to.figure("continuous_contribution_AR"))
}
```

`r if ('CA' %in% args$states) '#### California'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_CA"))){
  knitr::include_graphics(file.to.figure("continuous_contribution_CA"))
}
```

`r if ('CO' %in% args$states) '#### Colorado'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_CO"))){
knitr::include_graphics(file.to.figure("continuous_contribution_CO"))
}
```

`r if ('CT' %in% args$states) '#### Connecticut'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_CT"))){
knitr::include_graphics(file.to.figure("continuous_contribution_CT"))
}
```

`r if ('DE' %in% args$states) '#### Delaware'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_DE"))){
knitr::include_graphics(file.to.figure("continuous_contribution_DE"))
}
```

`r if ('DC' %in% args$states) '#### District of Columbia'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_DC"))){
knitr::include_graphics(file.to.figure("continuous_contribution_DC"))
}
```

`r if ('FL' %in% args$states) '#### Florida'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_FL"))){
knitr::include_graphics(file.to.figure("continuous_contribution_FL"))
}
```

`r if ('GA' %in% args$states) '#### Georgia'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_GA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_GA"))
}
```

`r if ('HI' %in% args$states) '#### Hawaii'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_HI"))){
knitr::include_graphics(file.to.figure("continuous_contribution_HI"))
}
```

`r if ('ID' %in% args$states) '#### Indiana'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_ID"))){
knitr::include_graphics(file.to.figure("continuous_contribution_ID"))
}
```

`r if ('IL' %in% args$states) '#### Illinois'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_IL"))){
knitr::include_graphics(file.to.figure("continuous_contribution_IL"))
}
```

`r if ('IN' %in% args$states) '#### Indiana'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_IN"))){
knitr::include_graphics(file.to.figure("continuous_contribution_IN"))
}
```

`r if ('IA' %in% args$states) '#### Iowa'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_IA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_IA"))
}
```

`r if ('KS' %in% args$states) '#### Kansas'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_KS"))){
knitr::include_graphics(file.to.figure("continuous_contribution_KS"))
}
```

`r if ('KY' %in% args$states) '#### Kentucky'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_KY"))){
knitr::include_graphics(file.to.figure("continuous_contribution_KY"))
}
```

`r if ('LA' %in% args$states) '#### Louisiana'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_LA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_LA"))
}
```

`r if ('ME' %in% args$states) '#### Maine'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_ME"))){
knitr::include_graphics(file.to.figure("continuous_contribution_ME"))
}
```

`r if ('MD' %in% args$states) '#### Maryland'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MD"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MD"))
}
```

`r if ('MA' %in% args$states) '#### Massachusetts'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MA"))
}
```

`r if ('MI' %in% args$states) '#### Michigan'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MI"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MI"))
}
```

`r if ('MN' %in% args$states) '#### Minnesota'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MN"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MN"))
}
```

`r if ('MS' %in% args$states) '#### Mississippi'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MS"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MS"))
}
```

`r if ('MO' %in% args$states) '#### Missouri'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MO"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MO"))
}
```

`r if ('MT' %in% args$states) '#### Montana'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_MT"))){
knitr::include_graphics(file.to.figure("continuous_contribution_MT"))
}
```

`r if ('NE' %in% args$states) '#### Nebraska'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NE"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NE"))
}
```

`r if ('NV' %in% args$states) '#### Nevada'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NV"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NV"))
}
```

`r if ('NH' %in% args$states) '#### New Hampshire'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NH"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NH"))
}
```

`r if ('NJ' %in% args$states) '#### New Jersey'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NJ"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NJ"))
}
```

`r if ('NM' %in% args$states) '#### New Mexico'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NM"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NM"))
}
```

`r if ('NY' %in% args$states) '#### New York'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NY"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NY"))
}
```

`r if ('NYC' %in% args$states) '#### New York City'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NYC"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NYC"))
}
```

`r if ('NC' %in% args$states) '#### North Carolina'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_NC"))){
knitr::include_graphics(file.to.figure("continuous_contribution_NC"))
}
```

`r if ('ND' %in% args$states) '#### North Dakota'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_ND"))){
knitr::include_graphics(file.to.figure("continuous_contribution_ND"))
}
```

`r if ('OH' %in% args$states) '#### Ohio'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_OH"))){
knitr::include_graphics(file.to.figure("continuous_contribution_OH"))
}
```

`r if ('OK' %in% args$states) '#### Oklahoma'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_OK"))){
knitr::include_graphics(file.to.figure("continuous_contribution_OK"))
}
```

`r if ('OR' %in% args$states) '#### Oregon'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_OR"))){
knitr::include_graphics(file.to.figure("continuous_contribution_OR"))
}
```

`r if ('PA' %in% args$states) '#### Pennsylvania'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_PA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_PA"))
}
```

`r if ('RI' %in% args$states) '#### Rhode Island'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_RI"))){
knitr::include_graphics(file.to.figure("continuous_contribution_RI"))
}
```

`r if ('SC' %in% args$states) '#### South Carolina'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_SC"))){
knitr::include_graphics(file.to.figure("continuous_contribution_SC"))
}
```

`r if ('SD' %in% args$states) '#### South Dakota'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_SD"))){
knitr::include_graphics(file.to.figure("continuous_contribution_SD"))
}
```

`r if ('TN' %in% args$states) '#### Tennessee'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_TN"))){
knitr::include_graphics(file.to.figure("continuous_contribution_TN"))
}
```

`r if ('TX' %in% args$states) '#### Texas'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_TX"))){
knitr::include_graphics(file.to.figure("continuous_contribution_TX"))
}
```

`r if ('UT' %in% args$states) '#### Utah'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_UT"))){
knitr::include_graphics(file.to.figure("continuous_contribution_UT"))
}
```

`r if ('VT' %in% args$states) '#### Vermont'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_VT"))){
knitr::include_graphics(file.to.figure("continuous_contribution_VT"))
}
```

`r if ('VA' %in% args$states) '#### Virginia'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_VA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_VA"))
}
```

`r if ('WA' %in% args$states) '#### Washington'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_WA"))){
knitr::include_graphics(file.to.figure("continuous_contribution_WA"))
}
```

`r if ('WV' %in% args$states) '#### West Virginia'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_WV"))){
knitr::include_graphics(file.to.figure("continuous_contribution_WV"))
}
```

`r if ('WI' %in% args$states) '#### Wisconsin'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_WI"))){
knitr::include_graphics(file.to.figure("continuous_contribution_WI"))
}
```

`r if ('WY' %in% args$states) '#### Wyoming'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("continuous_contribution_WY"))){
knitr::include_graphics(file.to.figure("continuous_contribution_WY"))
}
```



## Convergence diagnostics {.tabset .tabset-fade}

Listed below are the parameters with an effective sample size smaller than 500.

`r if ('AL' %in% args$states) '### Alabama'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AL"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AL"))
  neff[which(neff<500)]
}
```

`r if ('AK' %in% args$states) '### Alaska'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AK"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AK"))
  neff[which(neff<500)]
}
```

`r if ('AZ' %in% args$states) '### Arizona'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AZ"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AZ"))
  neff[which(neff<500)]
}
```

`r if ('AR' %in% args$states) '### Arkansas'`
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_AR"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_AR"))
  neff[which(neff<500)]
}
```

`r if ('CA' %in% args$states) '### California'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CA"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_CA"))
  neff[which(neff<500)]
}
```

`r if ('CO' %in% args$states) '### Colorado'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CO"))){
  neff <- readRDS(file.to.table("eff_sample_size_cum_CO"))
  neff[which(neff<500)]
}
```

`r if ('CT' %in% args$states) '### Connecticut'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_CT"))){
 neff <- readRDS(file.to.table("eff_sample_size_cum_CT"))
  neff[which(neff<500)]
}
```

`r if ('DE' %in% args$states) '### Delaware'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_DE"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_DE"))
  neff[which(neff<500)]
}
```

`r if ('DC' %in% args$states) '### District of Columbia'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_DC"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_DC"))
  neff[which(neff<500)]
}
```

`r if ('FL' %in% args$states) '### Florida'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_FL"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_FL"))
  neff[which(neff<500)]
}
```

`r if ('GA' %in% args$states) '### Georgia'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_GA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_GA"))
  neff[which(neff<500)]
}
```

`r if ('HI' %in% args$states) '### Hawaii'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_HI"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_HI"))
  neff[which(neff<500)]
}
```

`r if ('ID' %in% args$states) '### Indiana'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ID"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_ID"))
  neff[which(neff<500)]
}
```

`r if ('IL' %in% args$states) '### Illinois'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IL"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_IL"))
  neff[which(neff<500)]
}
```

`r if ('IN' %in% args$states) '### Indiana'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IN"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_IN"))
  neff[which(neff<500)]
}
```

`r if ('IA' %in% args$states) '### Iowa'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_IA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_IA"))
  neff[which(neff<500)]
}
```

`r if ('KS' %in% args$states) '### Kansas'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_KS"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_KS"))
  neff[which(neff<500)]
}
```

`r if ('KY' %in% args$states) '### Kentucky'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_KY"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_KY"))
  neff[which(neff<500)]
}
```

`r if ('LA' %in% args$states) '### Louisiana'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_LA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_LA"))
  neff[which(neff<500)]
}
```

`r if ('ME' %in% args$states) '### Maine'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ME"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_ME"))
  neff[which(neff<500)]
}
```

`r if ('MD' %in% args$states) '### Maryland'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MD"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MD"))
  neff[which(neff<500)]
}
```

`r if ('MA' %in% args$states) '### Massachusetts'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MA"))
  neff[which(neff<500)]
}
```

`r if ('MI' %in% args$states) '### Michigan'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MI"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MI"))
  neff[which(neff<500)]
}
```

`r if ('MN' %in% args$states) '### Minnesota'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MN"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MN"))
  neff[which(neff<500)]
}
```

`r if ('MS' %in% args$states) '### Mississippi'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MS"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MS"))
  neff[which(neff<500)]
}
```

`r if ('MO' %in% args$states) '### Missouri'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MO"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MO"))
  neff[which(neff<500)]
}
```

`r if ('MT' %in% args$states) '### Montana'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_MT"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_MT"))
  neff[which(neff<500)]
}
```

`r if ('NE' %in% args$states) '### Nebraska'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NE"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NE"))
  neff[which(neff<500)]
}
```

`r if ('NV' %in% args$states) '### Nevada'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NV"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NV"))
  neff[which(neff<500)]
}
```

`r if ('NH' %in% args$states) '### New Hampshire'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NH"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NH"))
  neff[which(neff<500)]
}
```

`r if ('NJ' %in% args$states) '### New Jersey'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NJ"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NJ"))
  neff[which(neff<500)]
}
```

`r if ('NM' %in% args$states) '### New Mexico'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NM"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NM"))
  neff[which(neff<500)]
}
```

`r if ('NY' %in% args$states) '### New York'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NY"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NY"))
  neff[which(neff<500)]
}
```

`r if ('NYC' %in% args$states) '### New York City'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NYC"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NYC"))
  neff[which(neff<500)]
}
```

`r if ('NC' %in% args$states) '### North Carolina'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_NC"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_NC"))
  neff[which(neff<500)]
}
```

`r if ('ND' %in% args$states) '### North Dakota'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_ND"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_ND"))
  neff[which(neff<500)]
}
```

`r if ('OH' %in% args$states) '### Ohio'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OH"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_OH"))
  neff[which(neff<500)]
}
```

`r if ('OK' %in% args$states) '### Oklahoma'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OK"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_OK"))
  neff[which(neff<500)]
}
```

`r if ('OR' %in% args$states) '### Oregon'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_OR"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_OR"))
  neff[which(neff<500)]
}
```

`r if ('PA' %in% args$states) '### Pennsylvania'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_PA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_PA"))
  neff[which(neff<500)]
}
```

`r if ('RI' %in% args$states) '### Rhode Island'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_RI"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_RI"))
  neff[which(neff<500)]
}
```

`r if ('SC' %in% args$states) '### South Carolina'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_SC"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_SC"))
  neff[which(neff<500)]
}
```

`r if ('SD' %in% args$states) '### South Dakota'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_SD"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_SD"))
  neff[which(neff<500)]
}
```

`r if ('TN' %in% args$states) '### Tennessee'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_TN"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_TN"))
  neff[which(neff<500)]
}
```

`r if ('TX' %in% args$states) '### Texas'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_TX"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_TX"))
  neff[which(neff<500)]
}
```

`r if ('UT' %in% args$states) '### Utah'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_UT"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_UT"))
  neff[which(neff<500)]
}
```

`r if ('VT' %in% args$states) '### Vermont'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_VT"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_VT"))
  neff[which(neff<500)]
}
```

`r if ('VA' %in% args$states) '### Virginia'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_VA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_VA"))
  neff[which(neff<500)]
}
```

`r if ('WA' %in% args$states) '### Washington'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WA"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_WA"))
  neff[which(neff<500)]
}
```

`r if ('WV' %in% args$states) '### West Virginia'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WV"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_WV"))
  neff[which(neff<500)]
}
```

`r if ('WI' %in% args$states) '### Wisconsin'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WI"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_WI"))
  neff[which(neff<500)]
}
```

`r if ('WY' %in% args$states) '### Wyoming'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.table("eff_sample_size_cum_WY"))){
neff <- readRDS(file.to.table("eff_sample_size_cum_WY"))
  neff[which(neff<500)]
}
```



